Meta-analysis

### 2020-05-29 04_MetaAnalysis.Rmd
Variation in grain.yield metafor outcome. Trying numerous iterations and Plotting them

# Data
slimmer_PM_dat <- read.csv("cache/slimmer_PM_clusterdat.csv"
)
```

@@

The first table in this output shows the tau^2 (variance) of each random effects and the number of occurances for each treatment in the analysis. The second table is in two parts(left and right). The left part indicates the level of acceptable rho (variation) when comparing treatments. All comparisons were acceptable except for a comparison between `Early` and `Late_plus`, `0.000` rho. `Early` and `Late_plus` treatments never occured within the same trial which is indicated by the right side of the table.

@@

First we will format the results into a dataframe and back-transform the log values by using the exponent function
```{r metafor_results}
results_AI <- data.frame(cbind(exp(PM_mv_AI$b),
                               exp((PM_mv_AI$ci.lb)),
                               exp(PM_mv_AI$ci.ub)))

>>>>

# Data
slimmer_PM_dat <- read.csv("cache/slimmer_PM_clusterdat.csv")
```

@@

```{r ReRunMetafor}
dat1 <- data.frame(
   iteration = 0,
   mods = names(coef(PM_mv_AI)),
   coefs = coef(PM_mv_AI),
   se = PM_mv_AI$se,
   zval = PM_mv_AI$zval,
   pval = PM_mv_AI$pval,
   ci.lb = PM_mv_AI$ci.lb,
   ci.ub = PM_mv_AI$ci.ub,
   row.names = NULL
   )

# Each time below is run dat1 will add the extra iterations to the bottom of dat1

for(i2 in (max(dat1$iteration) +1):(max(dat1$iteration) +3)){
   # Read in data again
slimmer_PM_dat <- read.csv("cache/slimmer_PM_clusterdat.csv")

# Identify trials without variance
TrialMSQ <- slimmer_PM_dat %>%
   group_by(trial_ref,location,year)%>%
   summarise(unique(Y_Msquare))

# impute variance
for (i in TrialMSQ[is.na(TrialMSQ$`unique(Y_Msquare)`), ]$trial_ref) {
   slimmer_PM_dat[slimmer_PM_dat$trial_ref == i, "Y_Msquare"] <-
      exp(rnorm(
         n = 1,
         mean = mean(log(TrialMSQ$`unique(Y_Msquare)`), na.rm = TRUE),
         sd(log(TrialMSQ$`unique(Y_Msquare)`), na.rm = TRUE)
      ))
}

#######

#reformat data
slimmer_PM_dat$yi <- log(slimmer_PM_dat$grain_yield.t.ha)
slimmer_PM_dat$vi <-
   slimmer_PM_dat$Y_Msquare / (slimmer_PM_dat$n * slimmer_PM_dat$grain_yield.t.ha ^
                                  2)

slimmer_PM_dat$spray_management <-
   factor(slimmer_PM_dat$spray_management)
slimmer_PM_dat$trial_ref <- factor(slimmer_PM_dat$trial_ref)
slimmer_PM_dat$trial <- factor(slimmer_PM_dat$trial)

# Run meta-analysis
PM_mv_AI <- rma.mv(
   yi,
   vi,
   mods = ~ spray_management,
   method = "ML",
   random = list(~ spray_management | trial),
   struct = "UN",
   data = slimmer_PM_dat
)

dat2 <- data.frame(
   iteration = i2,
   mods = names(coef(PM_mv_AI)),
   coefs = coef(PM_mv_AI),
   se = PM_mv_AI$se,
   zval = PM_mv_AI$zval,
   pval = PM_mv_AI$pval,
   ci.lb = PM_mv_AI$ci.lb,
   ci.ub = PM_mv_AI$ci.ub,
   row.names = NULL
   )

dat1 <- rbind(dat1,dat2)
}
dat1

```
```{r}
dat1 %>%
   ggplot(aes(x = iteration ,y = coefs,))+
   geom_ribbon(aes(ymax = ci.ub, ymin = ci.lb, x = iteration), fill = "grey70")+
   geom_line()+
   facet_grid(cols = vars(mods))

The first table in this output shows the tau^2 (variance) of each random effects and the number of occurrences for each treatment in the analysis. The second table is in two parts(left and right). The left part indicates the level of acceptable rho (variation) when comparing treatments. All comparisons were acceptable except for a comparison between `Early` and `Late_plus`, `0.000` rho. `Early` and `Late_plus` treatments never occured within the same trial which is indicated by the right side of the table.

@@

First we will format the results into a data frame and back-transform the log values by using the exponent function
```{r metafor_results}
results_AI <- data.frame(cbind(exp(PM_mv_AI$b),
                               exp((PM_mv_AI$ci.lb)),
                               exp(PM_mv_AI$ci.ub)))
